Tutorial_3

### 2024-09-17 Tutorial_3.Rmd
add code to compare model outputs

>>>>

# Compare MLE estimates from model_M3_f with the posterior mean estimates from model_M3

```{r load-models}
model_M3 <- readRDS("Tutorial_2_Bayesian/models/model_M3.rds")
load("Tutorial_3_Frequentist/model_M3_f.RData")
```

```{r extract-estimates}
est <- tibble(brm = fixef(model_M3)[,1],
              glmer = fixef(model_M3_f),
              effects = names(fixef(model_M3_f))) 
```

```{r plot-estimates}
cols    <- c( "c1" = "#ff00ff", "c2" = "#3399ff" )
shapes  <- c("s1" = 16, "s2" = 17)

p1 <- ggplot(data = est, aes(x = effects))
p1 <- p1 + geom_point(aes( y = brm,  color = "c1", shape = "s1"))
p1 <- p1 + geom_point(aes( y = glmer, color = "c2", shape = "s2")) 
p1 <- p1 + labs( x = "Effects", y = "cloglog-hazard" )
p1 <- p1 + scale_color_manual(name = "Model", 
                                breaks = c("c1", "c2"), 
                                values = cols,
                                labels = c("brm", "glmer"))
p1 <- p1 + scale_shape_manual(name = "Model", 
                              breaks = c("s1", "s2"),
                              values = shapes,
                              labels = c("brm", "glmer")) +
   theme(panel.grid = element_blank(),
         panel.background = element_rect(fill="white",color="black"),
         legend.position = "top",
         axis.text.x = element_text(angle=90)) 
p1
```
